\LARGE \bf {\sc underworlds}: Cascading Situation Assessment for Robots

### 2018-02-26 paper.tex
Update on Overleaf.

This work has been supported by the EU H2020 Marie Sk\l odowska-Curie Actions
project DoRoThy (grant 657227),  the EU H2020 MuMMER project (grant TODO LAAS)
and the EU H2020 L2TOR project (grant 688014).

>>>>

This work has been supported by the EU H2020 Marie Sk\l odowska-Curie Actions
project DoRoThy (grant 657227),  the EU H2020 MuMMER project (grant 688147)
and the EU H2020 L2TOR project (grant 688014).
